An open source scientific article about extrasolar magma oceans

### 2022-08-02 src/tex/ms.tex
include file endings for figures
define likelihood function

\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/flowchart}
        \caption{Workflow of our hypothesis testing with Bioverse. In the first block, a stellar sample is generated based on XXX. The stars are then populated with planets from XXX, which may be assigned a magma ocean based on the model described in Sect.~\ref{sec:mo_model}. The planets' respective transit probabilities are computed. The second block simulates the exoplanet survey whereby selection effects and detection biases are introduced. Finally, the third block deals with testing a hypothesis based on the data from the simulated survey. By iterating through these steps, we compute the statistical power of testing the hypothesis given the assumed survey design.}
        \label{fig:flowchart}
    \end{centering}
\end{figure*}

@@

\subsection{Synthetic planet populations with and without magma oceans}
\todo{describe the way we inject magma oceans into the synthetic planet population with Bioverse}
\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/has_magmaocean}
        \caption{Synthetic planets with and without magmaoceans as a function of Solar-equivalent semi-major axis}
        \label{fig:has_magmaocean}
    \end{centering}
\end{figure*}

>>>>

\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/flowchart.pdf}
        \caption{Workflow of our hypothesis testing with Bioverse. In the first block, a stellar sample is generated based on XXX. The stars are then populated with planets from XXX, which may be assigned a magma ocean based on the model described in Sect.~\ref{sec:mo_model}. The planets' respective transit probabilities are computed. The second block simulates the exoplanet survey whereby selection effects and detection biases are introduced. Finally, the third block deals with testing a hypothesis based on the data from the simulated survey. By iterating through these steps, we compute the statistical power of testing the hypothesis given the assumed survey design.}
        \label{fig:flowchart}
    \end{centering}
\end{figure*}

@@

\subsubsection{Definition of the magma ocean hypothesis and null hypothesis}
\todo{Define the null and alternative hypotheses}
...

For the likelihood function, we assumed that the planet radii $R_{\mathrm{P}, i}$ are measured with a normally distributed uncertainty $\sigma_{R_\mathrm{P}, i}$ and adopted a normal distribution
\begin{equation}
\mathcal{L}(R_\mathrm{P} \mid \boldsymbol{\theta})=\prod_{i}^{N} \frac{1}{\sqrt{2 \pi \sigma_{R_\mathrm{P}, i}^{2}}} \exp \left(-\frac{\left(R_{\mathrm{P}, i}-h\left(\boldsymbol{\theta}, a_{\mathrm{eff}, i}\right)\right)^{2}}{2 \sigma_{R_\mathrm{P}, i}^{2}}\right).
\end{equation}
Here, $h\left(\boldsymbol{\theta}, a_{\mathrm{eff}, i}\right)$ corresponds to the functional form of the magma ocean hypothesis\todo{link to eqn defining the hypothesis} .
We tested this hypothesis against the null hypothesis $h_\mathrm{null} (\theta, R_\mathrm{P}) = \theta$, which states that there is no relationship between the measured planet radii and (scaled) semi-major axes.

\subsection{Synthetic planet populations with and without magma oceans}
\todo{describe the way we inject magma oceans into the synthetic planet population with Bioverse}
\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/has_magmaocean.pdf}
        \caption{Synthetic planets with and without magmaoceans as a function of Solar-equivalent semi-major axis}
        \label{fig:has_magmaocean}
    \end{centering}
\end{figure*}
